---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

What makes you happy? Do people feel happy due to similar reason? why or why not? Do different populations (eg. female vs. male, teenager vs. adult) have different sources of happiness? What other factors may affect people's decription of their happiness? To answer these question, I use HappyDB data which "is a corpus of 100,000 crowd-sourced happy moments, aims to advance the state of the art of understanding the causes of happiness that can be gleaned from text." I used 94513 happy moments collected from 9972 distinct workers to take a deeper look at data and try to answer these questions.
```{r echo=TRUE,warning=FALSE, message=FALSE}
library(tm)
library(tidytext)
library(tidyverse)
library(DT)
```

```{r}
urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/cleaned_hm.csv'
hm_data <- read_csv(urlfile)
```

```{r}
corpus <- VCorpus(VectorSource(hm_data$cleaned_hm))%>%
  tm_map(content_transformer(tolower))%>%
  tm_map(removePunctuation)%>%
  tm_map(removeNumbers)%>%
  tm_map(removeWords, character(0))%>%
  tm_map(stripWhitespace)
```

```{r}
stemmed <- tm_map(corpus, stemDocument) %>%
  tidy() %>%
  select(text)
```

```{r}
dict <- tidy(corpus) %>%
  select(text) %>%
  unnest_tokens(dictionary, text)

```

```{r}
data("stop_words")
word <- c("happy","ago","yesterday","lot","today","months","month",
                 "happier","happiest","last","week","past","day","time","moment")
stop_words <- stop_words %>%
  bind_rows(mutate(tibble(word), lexicon = "updated"))
```


```{r}
completed <- stemmed %>%
  mutate(id = row_number()) %>%
  unnest_tokens(stems, text) %>%
  bind_cols(dict) %>%
  anti_join(stop_words, by = c("dictionary" = "word"))
```

```{r}
completed <- completed %>%
  group_by(stems) %>%
  count(dictionary) %>%
  mutate(word = dictionary[which.max(n)]) %>%
  ungroup() %>%
  select(stems, word) %>%
  distinct() %>%
  right_join(completed) %>%
  select(-stems)
```

```{r}
completed <- completed %>%
  group_by(id) %>%
  summarise(text = str_c(word, collapse = " ")) %>%
  ungroup()
```

```{r}
hm_data <- hm_data %>%
  mutate(id = row_number()) %>%
  inner_join(completed)
```


```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(tidytext)
library(DT)
library(scales)
library(wordcloud2)
library(gridExtra)
library(ngram)
library(shiny) 
```

```{r load data, warning=FALSE, message=FALSE}
urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/demographic.csv'
demo_data <- read_csv(urlfile)
```


```{r}
hm_data <- hm_data %>%
  inner_join(demo_data, by = "wid") %>%
  select(wid,
         original_hm,
         gender, 
         marital, 
         parenthood,
         reflection_period,
         age, 
         country, 
         ground_truth_category, 
         predicted_category,
         text) %>%
  mutate(count = sapply(hm_data$text, wordcount)) %>%
  filter(gender %in% c("m", "f")) %>%
  filter(marital %in% c("single", "married")) %>%
  filter(parenthood %in% c("n", "y")) %>%
  filter(reflection_period %in% c("24h", "3m")) %>%
  mutate(reflection_period = fct_recode(reflection_period, 
                                        months_3 = "3m", hours_24 = "24h"))
```


```{r}
nrow(hm_data)
length(unique(hm_data$wid))

```

#Part 1
From the wordcloud, we find that words like friends, family, game, birthday, and home are nouns that are most frequently used when people talked about their happiness. Verbs such as played, watched, enjoyed, bought, and love are frequently mentioned. 

#Part 2
Are sources of happiness influenced largely by time intervals? It is reasonable to expect that people tend to recall big events or impressive moments in 3-month interval, whereas detailed events and daily moments are more likely to appear in 24-hour interval.

We first use predicted_category that categorized different happy moments to see if there is a significant difference in categories of happiness between 3-month and 24-hour time interval.
```{r}
library(ggplot2)
hm_data_3m<-hm_data[hm_data$reflection_period=="months_3",]
hm_data_24h<-hm_data[hm_data$reflection_period=="hours_24",]
dtframe<-data.frame(table(hm_data_24h$predicted_category)-table(hm_data_3m$predicted_category))
colnames(dtframe)<-c("Category","Difference")
ggplot(dtframe,aes(x=Category,y=Difference))+
  geom_bar(stat="identity")
```

As we can see from the above histogram, people talk more about achievement and affection in 3-month interval, whereas enjoy the moent and leisure appears more in 24-hour interval. This illustrates the point made in the beginning of this part that achievemnet and affection are long-last memory and sentiment, whereas moment of life and leisure time are transitory.

Now let us look at frequecy of specific words for 24-hour and 3-month time intervals.
```{r}
hm_data_24h_bigram <- hm_data_24h %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  count(bigram,sort = TRUE)
head(hm_data_24h_bigram,10)

hm_data_3m_bigram <- hm_data_3m %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  count(bigram,sort = TRUE) 
head(hm_data_3m_bigram,10)


```

We can see from that in 24-hour period, people feel happy due to everyday events such as playing video game, watching movie, eating ice cream, talking to friends. On the other hand, in 3-month period, their happiness come from impressive big events like birthday party and buying a car. 

This result again answers the question in the very beginning of this section that sources of happiness depends on length of time period.

#Part 3
Next we want to investigate the relationship between happiness and gender. Does the causes of happiness differ between male and female?
```{r}
hm_data_m<-hm_data[hm_data$gender=="m",]
hm_data_f<-hm_data[hm_data$gender=="f",]
tablem<-round(table(hm_data_m$predicted_category)/nrow(hm_data_m)*100)
lbls <- paste(names(tablem), "\n", tablem, sep="")
lbls<- paste(lbls,"%",sep="") 
pie(tablem, labels = lbls, 
   main="Pie Chart of Male Happiness Category")
tablef<-round(table(hm_data_f$predicted_category)/nrow(hm_data_f)*100)
lblsf <- paste(names(tablef), "\n", tablef, sep="")
lblsf<- paste(lblsf,"%",sep="") 
pie(tablef, labels = lblsf, 
   main="Pie Chart of Female Happiness Category")
```

From an overall pie chart of happiness category, we see that female talk a lot more about affection (12% higher) while male talk more about achievement (7% higher).
```{r}
hm_data_m_bigram <- hm_data_m %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  count(bigram,sort = TRUE)
head(hm_data_m_bigram,10)
hm_data_f_bigram <- hm_data_f %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  count(bigram,sort = TRUE) 
head(hm_data_f_bigram,10)
```

We can conclude from the above list that playing video game("video game","played video","played game") ranks at the top of bigram list when males recall their happy moment, whereas ice cream rank at the top at female's list. Besides, both "watch movie" and "birthday party" rank as top words among both male's and female's list.


#Part 4
In this part, we want to investigate the relationship between happiness and age. A natural question to ask is that whether or not people from different life stages have difference source of happiness. To start the analysis, I divide the whole sample into three parts, namely yg(young adulthood) 17-35 years old, ma(middle adulthood) 36-55 years old, and la(late adulthood) 56+ years old.
```{r,message=FALSE, warning=FALSE}
hm_data_ya<-hm_data[as.numeric(hm_data$age)<=35&as.numeric(hm_data$age)>=17,]
hm_data_ma<-hm_data[as.numeric(hm_data$age)>=36&as.numeric(hm_data$age)<=55,]
hm_data_la<-hm_data[as.numeric(hm_data$age)>=56,]


table_ya_df<-data.frame(table(hm_data_ya$predicted_category)/nrow(hm_data_ya))
category_ya<-unique(table_ya_df$Var1)
ggplot(data=table_ya_df,aes(Var1,Freq,fill=category_ya))+
  geom_bar(stat="identity")+
  scale_y_continuous(labels = percent)+
  geom_text(data=table_ya_df, aes(x = Var1, y = Freq,
                                             label = paste0(round(Freq*100,2),"%")), size=4)
  
table_ma_df<-data.frame(table(hm_data_ma$predicted_category)/nrow(hm_data_ma))
category_ma<-unique(table_ma_df$Var1)
ggplot(table_ma_df,aes(Var1,Freq,fill=category_ma))+
  geom_bar(stat="identity")+
  scale_y_continuous(labels = percent)+
  geom_text(data=table_ma_df, aes(x = Var1, y = Freq,
                                             label = paste0(round(Freq*100,2),"%")), size=4)
table_la_df<-data.frame(table(hm_data_la$predicted_category)/nrow(hm_data_la))
category_la<-unique(table_la_df$Var1)
ggplot(table_la_df,aes(Var1,Freq,fill=category_la))+
  geom_bar(stat="identity")+
  scale_y_continuous(labels = percent)+
  geom_text(data=table_la_df, aes(x = Var1, y = Freq,
                                             label = paste0(round(Freq*100,2),"%")), size=4)


```

One can find from three bar charts that no matter how old you are, your happiness mainly comes from achievement and affection. However, an interesting trend is that percentage of happiness comes from achievement drops about 2 percents when people step into next life stage. This is reasonable in a sense that when you are young, you are more likely to achieve something or get a sense of achievement than adults and seniors do.

Another trend is that as people grow, they gain more happiness from affection, with someone they love, but less of their happiness comes from bonding. This might be explained by the fact that when people get older, they care more about their family, and when they are young, they usually spend more time with friends.

#Part 5 Summary
In conclusion, by analyzing 100,000 happy moments, we get the following result.
1.Words like friends, family, game, birthday, and home are most commonly used words when people recall their happy moment. 
2.Reflection period is an influetial factor to source of happiness. People tend to recall big events when they are asked about happy moments in past 3 month, whereas people tend to recall detailed and daily event when tehy are asked about happy moments in past 24 hours.
3. Females are less likely to feel happy about achievement than males do, but females are more likely to feel happy about affection.
4. Achievement and affection are main sources of happiness for the whole population. Teenagers or young adults usually gain more happiness from achievemnt than adults and seniors do.As one gets older, he or she gains more happiness from affection, but less from bonding.